---
title: "Day-3 (Counts)"
author: "Anusha"
---

```{r}
#| label: setup
library(tidyverse)
library(mosaic)
library(ggformula)
library(skimr)
```

## Data set of taxis rides in Chicago

```{r}
taxi <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/modeldata/taxi.csv")
taxi
```

```{r}
glimpse(taxi)
```

```{r}
inspect(taxi)
```

```{r}
skimr::skim(taxi)
```

#### Converting some variables into ordinal variables (ord) \~ Data Munging

> Converting dow, local, month and tip into ord.

```{r}
taxi_modified <- taxi %>%
  dplyr::mutate(
    dow = factor(dow,
      levels = c("Mon", "Tue","Wed", "Thu", "Fri", "Sat", "Sun"),
      labels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      ordered = TRUE
    ),
    ##
    local = factor(local,
      levels = c("no", "yes"),
      labels = c("no", "yes"),
      ordered = TRUE
    ),
    ##
    month = factor(month,
      levels = c("Jan", "Feb", "Mar", "Apr"),
      labels = c("Jan", "Feb", "Mar", "Apr"),
      ordered = TRUE
    ),
    ##
    tip = factor(tip,
      levels = c("no", "yes"),
      labels = c("no", "yes"),
      ordered = TRUE
    ),
    hour = as_factor(hour)
  )
glimpse(taxi_modified)
```

> Do more people **tip** than not?
>
> > People do tip more.

```{r}
##theme_set(new = theme_custom())
##
gf_bar(~tip, data = taxi_modified) %>% 
  gf_labs(title = "Plot 1A: Counts of Tips")
```

> Does the **tip** depend upon whether the trip is **local** or not?
>
> > Yes, the depends on whether the ride was local or not.

```{r}
taxi_modified %>%
  gf_bar(~local,
    fill = ~tip,
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart")

```

> > Comparitive graph to get a clear answer.

```{r}
taxi_modified %>%
  gf_bar(~tip,
    color = ~local,
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart")
```

Trying another code to plot with different colours:

```{r}
taxi_modified %>%
  gf_bar(~local,
    fill = ~tip,
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart") %>% 
  gf_refine(scale_fill_manual(values = c("powderblue", "pink")))
```

> > -   People tip more when the trip is not local.

```{r}
taxi_modified %>%
  gf_bar(~local,
    fill = ~tip,
    position = "stack"
  ) %>%
  gf_labs(title = "Plot 2B: Stacked Bar Chart",
          subtitle = "Can we spot per group differences in proportions??") %>% 
  gf_refine(scale_fill_manual(values = c("powderblue", "pink")))
```

> > -   The below graph is more accurate, and tells us the same that, people tip more when the trip is non local.

```{r}
taxi_modified %>%
  gf_bar(~local,
    fill = ~tip,
    position = "fill"
  ) %>%
  gf_labs(title = "Plot 2C: Filled Bar Chart",
          subtitle = "Shows Per group differences in Proportions!") %>% 
  gf_refine(scale_fill_manual(values = c("powderblue", "pink")))
```

> Do some cab **companies** get more **tips** than others?
>
> > -   Here, we see 'Flash Cab' gets the least amount of tips.
> >
> > -   'Chicago Independents' get the most tips.

```{r}
taxi_modified %>%
  gf_bar(~company, fill = ~tip, position = "fill") %>%
  gf_labs(
    title = "Plot 2D: Filled Bar Chart",
    subtitle = "Shows Per group differences in Proportions!"
  ) %>%
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1))) %>% 
 gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

> Does a **tip** depend upon the *distance*, *hour of the day*, *dow* and *month* ?
>
> > -   By hour :
> >
> >     -   2 am and 4 am gets the most tips.

```{r}
gf_bar(~hour, fill = ~tip, data = taxi_modified) %>%
  gf_labs(title = "Plot B: Counts of Tips by Hour") %>% 
  gf_refine(scale_fill_manual(values = c("violet", "pink"))) 

```

```{r}
gf_bar(~hour, fill = ~tip, 
       position = "fill",
       data = taxi_modified) %>%
  gf_labs(title = "Plot B: Counts of Tips by Hour") %>% 
  gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

-   By dow:

    -   Thursdays and Sundays get more tips.

```{r}
gf_bar(~dow, fill = ~tip, data = taxi_modified) %>%
  gf_labs(title = "Plot C: Counts of Tips by Day of Week") %>% 
  gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

```{r}
gf_bar(~dow, fill = ~tip, 
       position = "fill",
       data = taxi_modified) %>%
  gf_labs(title = "Plot C: Counts of Tips by Day of Week") %>% 
  gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

-   By month:

    -   April gets the most tips.

```{r}
gf_bar(~month, fill = ~tip, data = taxi_modified) %>%
  gf_labs(title = "Plot D: Counts of Tips by Month") %>% 
gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

```{r}
gf_bar(~month, fill = ~tip,
       position = "fill",
       data = taxi_modified) %>%
  gf_labs(title = "Plot D: Counts of Tips by Month") %>% 
gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

> > This plot gives inoformation on the tips collected on each day of each month.

```{r}
gf_bar(~ month | dow, fill = ~tip, data = taxi_modified) %>%
  gf_labs(title = "Plot E: Counts of Tips by Day of Week and Month")%>% 
gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

```{r}
gf_bar(~ dow | hour, fill = ~tip, 
       position = "fill",
       data = taxi_modified) %>%
  gf_labs(
    title = "Plot F: Counts of Tips by Hour and Day of Week",
    subtitle = "Is this plot arrangement easy to grasp?"
  )%>% 
   gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1))) %>% 
   gf_theme(theme(axis.text.y.left = element_text(size = 4, angle = 45, hjust = 1))) %>% 
gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

> > This plot give a more detailed information on tipping on the hour of each specific day of the week.

```{r}
gf_bar(~ hour | dow, fill = ~tip, data = taxi_modified) %>%
  gf_labs(
    title = "Plot G: Counts of Tips by Hour and Day of Week",
    subtitle = "Swapped the Facets"
  ) %>% 
  gf_theme(theme(axis.text.x = element_text(size = 4, angle = 45, hjust = 1))) %>%
  gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

### Addiction Data set - 'HELPrct'

```{r}
data("HELPrct")
HELPrct
```

```{r}
HELPrct %>% gf_bar(~substance)
```

Plotting based on sex:

```{r}
HELPrct %>% gf_props(~substance, fill = ~sex) %>% 
  gf_refine(scale_fill_manual(values = c("violet", "pink"))) 
```

```{r}
gf_props(~substance,
  data = mosaicData::HELPrct, fill = ~sex,
  position = "dodge"
) %>%
  gf_labs(title = "Plotting Proportions using gf_props") %>% 
   gf_refine(scale_fill_manual(values = c("violet", "pink")))
```

```{r}
gf_props(~substance,
  data = mosaicData::HELPrct, fill = ~sex,
  position = "fill"
) %>% 
  gf_labs(title = "Plotting Proportions using gf_props") %>% 
    gf_refine(scale_fill_manual(values = c("violet", "pink")))
```

```{r}
gf_percents(~substance,
  data = mosaicData::HELPrct, fill = ~sex,
  position = "dodge"
) %>%
  gf_refine(
    scale_y_continuous(
      labels = scales::label_percent(scale = 1)
    )
  ) %>%
  gf_labs(title = "Plotting Percentages using gf_percents")%>% 
    gf_refine(scale_fill_manual(values = c("violet", "pink")))
```

# A 1

## "Your Turn"

-   I have chosen to work on the 'banned' data set (banned books) from 'Counts'.

```{r}
book <- read_delim(file = "../../Data/banned.csv", delim = "," )
book
```

```{r}
# book %>%
 # head(10) %>%
#  kbl(
    # add Human Readable column names
 #   col.names = c(
  ##    "Count of type of Ban", "Banned from classrooms", "Banned from libraries",
    #  "Banned from libraries & classrooms", "Banned Pending Investigation", "Grand Total"
    #),
#    caption = "Banned Books Dataset"
 # ) %>%
  #kable_styling(
    #bootstrap_options = c(
     # "striped", "hover",
     # "condensed", "responsive"
  #  ),
   # full_width = F, position = "center"
  #)
```

```{r}
glimpse(book)
```

```{r}
inspect(book)
```

```{r}
skim(book)
```

### Converting some variables into ordinal variables \~ Data Munging

> -   Converting 'Banned in Classrooms' (Column Labels) and 'Banned from Libraries and Classrooms' (..4) into ordinal variables.
>
> -   I am not converting the any other variable into factors because they have more levels.

```{r}
book_modified <- book %>%
  dplyr::mutate(
    `Column Labels` = as_factor(`Column Labels`),
    ...4 = as_factor(...4),
    ...3 = as_factor(...3),
    ...5 = as_factor(...5)
  )
```

```{r}
glimpse(book_modified)
```

```{r}
inspect(book_modified)
```

```{r}
skim(book_modified)
```

### Bar Graphs

> -   Plot of books banned in the classroom.
>
> -   1 book is banned from at least 5 classrooms.

```{r}
book_modified <- book_modified %>%
  dplyr::rename(classrooms = `Column Labels`)
book_modified %>% 
  drop_na(classrooms) %>%
gf_bar(~classrooms, fill = "lightyellow", color = "black") %>%
  gf_labs(title = "Plot 1A: Counts of books Banned from the classroom") 
```

> -   Plot for books banned in the classroom and in total for each state.
>
> -   In the Grand Total, 1 book is definitely banned more in classrooms.

```{r}

```

> -   Plot for books banned in libraries.
>
> -   There is 1 book definitely banned from libraries in 6 states.
>
> -   2 books are banned in 2 states.
>
> -   Several states have 1 to 2 books banned from libraries. This represents a relatively small number but still shows that the issue is widespread across many states.

```{r}
book_modified <- book_modified %>%
  dplyr::rename(libraries = `...3`)
book_modified %>% 
  drop_na(libraries) %>%
gf_bar(~libraries, fill = "lightyellow", color = "black") %>%
  gf_labs(title = "Plot 1A: Counts of books Banned from libraries")  
```

> -   Plot for books banned in libraries in total for each state.
>
> -   In the Grand Total, 1 book is definitely banned more in libraries.
>
> -   2 books are banned in some libraries across some states.

```{r}

```

> -   Plot for books banned in libraries and classrooms.
>
> -   1 book is mostly banned from both classrooms and libraries in 4 states.
>
> -   9 books are banned from both in 2 states.
>
> -   2 books are banned form both in 2 states.

```{r}
book_modified <- book_modified %>%
  dplyr::rename(both = `...5`)
book_modified %>% 
  drop_na(both) %>%
gf_bar(~both, fill = "lightyellow", color = "black") %>%
  gf_labs(title = "Plot 3A: Counts of books Banned from libraries and classrooms")
```

> -   Plot for banned in classrooms and libraries in total for each state.

```{r}

```
