---
title: "Day-2 (Summaries)"
author: "Anusha"
---

## Introduction

Today, I am working on Data Summaries. We are throwing away data to consolidate and summarize it.

### *Day-2 (27th Sept)*

```{r}
#| label: setup
library(tidyverse)
library(skimr)
library(mosaic)
library(knitr)
library(kableExtra)
library(babynames)
library(ggformula)
```

```{r}
mpg
```

First 10 rows of the data set.

> We use 'head' to get the first few elements in the data set.
>
> Similarly, 'tail' is used to get the last few elements in the data set.

```{r}
mpg %>% 
  head(10)
```

> Glimpse is a function in dplyr which is a part of the tidyverse package.

```{r}
mpg %>% dplyr::glimpse()
```

> Inspect is a function in the package mosaic.

```{r}
inspect(mpg)
```

> skim is function in skimr package.

```{r}
skimr::skim(mpg)
```

> Now, we change cyl, fl, drv, class and trans from an int to an ordinal variable called factor.

```{r}
mpg_modified <- mpg %>%
  dplyr::mutate(
    cyl = as_factor(cyl),
    fl = as_factor(fl),
    drv = as_factor(drv),
    class = as_factor(class),
    trans = as_factor(trans)
  )
glimpse(mpg_modified)
```

#### Trying out with a different set!

I imported the library "babynames" from the previous class.

```{r}
babynames
```

Converting 'sex' into an ordinal variable, factor.

```{r}
babynames_modified <- babynames %>%
  dplyr::mutate(
    sex = as_factor(sex),
  )
glimpse(babynames_modified)
```

> Glimpse:

```{r}
glimpse(babynames_modified)
```

> Inspect:

```{r}
inspect(babynames_modified)
```

> Skim:

```{r}
skimr::skim(babynames_modified)
```

### Coming back to mpg data set...

Groups and Summaries of Quantitative Variables

> Grouping by cyl:
>
> -   As the cyl increases, the average highway mileage reduces.

```{r}
mpg_modified %>%
  group_by(cyl) %>%
  summarize(average_hwy = mean(hwy), count = n())
```

> Grouping by cy and fl (here, fl is fuel):
>
> -   All combinations of both cyl and fl together.
>
> -   There are 4 levels of cyl and 5 levels of fl. So, there should be 20 combinations. But it is not 20 because certain cars do not have it.

```{r}
mpg_modified %>%
  group_by(cyl, fl) %>%
  summarize(average_hwy = mean(hwy), count = n())
```

> Grouping by manufacturer:

```{r}
mpg %>% group_by(manufacturer) %>% summarize(mean_mileage_Manuf = mean(hwy))
```

```{r}
mpg %>% group_by(manufacturer) %>% summarize(mean_mileage_Manuf2 = mean(cty))
```

### Math Anxiety Data set

> -   AMAS (Adult Manifest Anxiety Scale)
>
> -   RCMAS (Revised Children's Manifest Anxiety Scale)
>
> -   Arith (Arithmetic Subtest of Intelligence Tests)

```{r}
math_anxiety <- read_delim(file = "../../Data/MathAnxiety.csv", delim = ";" )
math_anxiety
```

> Glimpse:

```{r}
glimpse(math_anxiety)
```

> Inspect:

```{r}
inspect(math_anxiety)
```

> Skim:

```{r}
skimr::skim(math_anxiety)
```

> Converting certain variables into ordinal variables, that is factors.
>
> Converting 'Gender' and 'Grade' as factors.

```{r}
math_modified <- math_anxiety %>%
  dplyr::mutate(
     Grade = as_factor(Grade),
     Gender = as_factor(Gender),
     Arith = as_factor(Arith)
  )
glimpse(math_modified)
```

Modified Glimpse:

```{r}
glimpse(math_modified)
```

Modified Inspect:

```{r}
inspect(math_modified)
```

Modified Skim:

```{r}
skimr::skim(math_modified)
```

Mean value of the Anxiety in Boys and Girls in Primary and Secondary school

> Calculating Anxiety by grouping Gender:

```{r}
math_anxiety %>% group_by(Gender) %>% summarize(mean_anx1 = mean(AMAS), mean_anx2 = mean(RCMAS), count =n())
```

> Calculating Anxiety by grouping Grade:

```{r}
math_anxiety %>% group_by(Grade) %>% summarize(mean_anx1 = mean(AMAS), mean_anx2 = mean(RCMAS), count =n())

```

> Calculating Anxiety by grouping Gender and Grade:

```{r}
math_anxiety %>% group_by(Gender,Grade) %>% summarize(mean_anx1 = mean(AMAS), mean_anx2 = mean(RCMAS), count =n())
```

> Calculating Anxiety by grouping Gender, Grade and Arith:

```{r}
math_anxiety %>% group_by(Gender,Grade, Arith) %>% summarize(mean_anx1 = mean(AMAS), mean_anx2 = mean(RCMAS), count =n())
```
