---
title: "Day-2 (Summaries)"
author: "Anusha"
---

## Introduction

Today, I am working on Data Summaries. We are throwing away data to consolidate and summarize it.

### *Day-2 (27th Sept)*

```{r}
#| label: setup
library(tidyverse)
library(skimr)
library(mosaic)
library(knitr)
library(kableExtra)
library(babynames)
library(ggformula)
```

```{r}
mpg
```

First 10 rows of the data set.

> We use 'head' to get the first few elements in the data set.
>
> Similarly, 'tail' is used to get the last few elements in the data set.

```{r}
mpg %>% 
  head(10)
```

> Glimpse is a function in dplyr which is a part of the tidyverse package.

```{r}
mpg %>% dplyr::glimpse()
```

> Inspect is a function in the package mosaic.

```{r}
inspect(mpg)
```

> skim is function in skimr package.

```{r}
skimr::skim(mpg)
```

> Now, we change cyl, fl, drv, class and trans from an int to an ordinal variable called factor.

```{r}
mpg_modified <- mpg %>%
  dplyr::mutate(
    cyl = as_factor(cyl),
    fl = as_factor(fl),
    drv = as_factor(drv),
    class = as_factor(class),
    trans = as_factor(trans)
  )
glimpse(mpg_modified)
```

#### Trying out with a different set!

I imported the library "babynames" from the previous class.

```{r}
babynames
```

Converting 'sex' into an ordinal variable, factor.

```{r}
babynames_modified <- babynames %>%
  dplyr::mutate(
    sex = as_factor(sex),
  )
glimpse(babynames_modified)
```

> Glimpse:

```{r}
glimpse(babynames_modified)
```

> Inspect:

```{r}
inspect(babynames_modified)
```

> Skim:

```{r}
skimr::skim(babynames_modified)
```

### Coming back to mpg data set...

Groups and Summaries of Quantitative Variables

> Grouping by cyl:
>
> -   As the cyl increases, the average highway mileage reduces.

```{r}
mpg_modified %>%
  group_by(cyl) %>%
  summarize(average_hwy = mean(hwy), count = n())
```

> Grouping by cy and fl (here, fl is fuel):
>
> -   All combinations of both cyl and fl together.
>
> -   There are 4 levels of cyl and 5 levels of fl. So, there should be 20 combinations. But it is not 20 because certain cars do not have it.

```{r}
mpg_modified %>%
  group_by(cyl, fl) %>%
  summarize(average_hwy = mean(hwy), count = n())
```

> Grouping by manufacturer:

```{r}
mpg %>% group_by(manufacturer) %>% summarize(mean_mileage_Manuf = mean(hwy))
```

```{r}
mpg %>% group_by(manufacturer) %>% summarize(mean_mileage_Manuf2 = mean(cty))
```

# A 1

## "Your Turn"

-   I have chosen to work further on the *'Math Anxiety'* data set from 'Summaries'.

-   I played around with this data even further. To open the data set here, we use the command 'read_delim' since this data set is downloaded externally and excel would read the commas and semicolons. This command helps in ignoring these punctuation marks and organizing the data in columns.

-   Here, I have first used 'glimpse', 'inspect' and 'skim' to get an overview of the data and to easily understand which variable is quantitative and qualitative.

-   I have then converted necessary variables into a factor to make 'summarizing' it easier and more tactful.

-   Thereafter, I calculated the mean (average) anxiety of children based on gender, grade, gender & grade and gender, grade & arith.

### Math Anxiety Data set

> -   AMAS (Adult Manifest Anxiety Scale)
>
> -   RCMAS (Revised Children's Manifest Anxiety Scale)
>
> -   Arith (Arithmetic Sub test of Intelligence Tests)

```{r}
math_anxiety <- read_delim(file = "../../Data/MathAnxiety.csv", delim = ";" )
math_anxiety
```

> Glimpse:

```{r}
glimpse(math_anxiety)
```

> Inspect:

```{r}
inspect(math_anxiety)
```

> Skim:

```{r}
skimr::skim(math_anxiety)
```

### Converting certain variables into ordinal variables, that is factors.

> Converting Grade, Gender and Arith into factors.
>
> We use the 'mutate' function from the dplyr library to convert the variables.

```{r}
math_modified <- math_anxiety %>%
  dplyr::mutate(
     Grade = as_factor(Grade),
     Gender = as_factor(Gender),
     Arith = as_factor(Arith)
  )
```

Modified Glimpse:

```{r}
glimpse(math_modified)
```

Modified Inspect:

```{r}
inspect(math_modified)
```

Modified Skim:

```{r}
skimr::skim(math_modified)
```

#### Mean value of the Anxiety in Boys and Girls in Primary and Secondary school

1.  Here, mean_anx1 is AMAS and mean_anx2 is RCMAS.
2.  We uses group_by command to group a data by a specific variable.
3.  summarize is used to create a summary of the data by calculating specific aggregate statistics (eg. mean_anx1, mean_anx2)

> Calculating Anxiety by grouping Gender:
>
> -   We can infer that girls have more anxiety than boys.

```{r}
math_anxiety %>% group_by(Gender) %>% summarize(mean_anx1 = mean(AMAS), mean_anx2 = mean(RCMAS), count =n())
```

> Calculating Anxiety by grouping Grade:
>
> -   Secondary school students have more anxiety.

```{r}
math_anxiety %>% group_by(Grade) %>% summarize(mean_anx1 = mean(AMAS), mean_anx2 = mean(RCMAS), count =n())

```

> Calculating Anxiety by grouping Gender and Grade:
>
> -   Anxiety levels increase for both boys and girls as they move from primary to secondary school.
>
> -   Girls tend to have higher anxiety levels than boys in both primary and secondary school. Specifically:
>
>     -   In primary school, girls have a higher mean anxiety score (22.73 for mean_anx1, 20.65 for mean_anx2) compared to boys (20.95 for mean_anx1, 18.56 for mean_anx2).
>
>     -   In secondary school, the same pattern holds, with girls having higher mean anxiety scores (23.49 for mean_anx1, 20.30 for mean_anx2) than boys (21.52 for mean_anx1, 17.40 for mean_anx2).
>
> -   Boys show a slight increase in anxiety (mean_anx1) from primary to secondary school, but a slight decrease in mean_anx2. Girls show a clearer increase in mean_anx1 as they move to secondary school.
>
> -   The comparison in secondary school is less balanced due to the lower number of girls, which may affect the robustness of those conclusions.

```{r}
math_anxiety %>% group_by(Gender,Grade) %>% summarize(mean_anx1 = mean(AMAS), mean_anx2 = mean(RCMAS), count =n())
```

> Calculating Anxiety by grouping Gender, Grade and Arith:
>
> -   In primary school, anxiety levels (mean_anx1 and mean_anx2) tend to be higher in lower arithmetic levels (particularly Arith 2), and they decrease as boys progress to higher levels (Arith 7 and Arith 8).
>
> -   Primary school girls generally exhibit increasing anxiety levels up to Arith 6, after which anxiety decreases.
>
> -   Secondary school girls exhibit consistently higher anxiety levels compared to primary school girls, with particularly high levels in early arithmetic stages.

```{r}
math_anxiety %>% group_by(Gender,Grade, Arith) %>% summarize(mean_anx1 = mean(AMAS), mean_anx2 = mean(RCMAS), count =n())
```
