---
title: "Class-5(Groups)"
author: "Anusha"
date: "10-10-24"
---

# Day-5 (Groups)

# Part one

## Introduction

*Today we are working with groups. 'Groups' are good to get information on how the data can be categorized and on what basis these groups are created*.

*So, today we will be playing around with 'gf_boxplot'. This helps in identifying a range and the median of some qual variable.*

Let's start our coding for today!

```{r}
#| label : setup
library(tidyverse)
library(mosaic)
library(ggformula)
library(skimr)
library(crosstable)
library(palmerpenguins)
```

### Case Study - 1 (gss_wages data set)

```{r}
wages <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/stevedata/gss_wages.csv")
glimpse(wages)
```

```{r}
skim(wages)
```

```{r}
inspect(wages)
```

-   We will convert some of these variables into ordinal variables, i.e, factor/ord \~ **Data Munging**

```{r}
wages_again <- wages %>% 
  mutate(
    gender = as_factor(gender),
    educcat = as_factor(educcat),
    maritalcat = as_factor(maritalcat),
    wrkstat = as_factor(wrkstat),
    occrecode = as_factor(occrecode)
  )
wages_again %>% glimpse()
```

```{r}
wages_clean <-
  wages_again %>%
  tidyr::drop_na(realrinc) # choose column or leave blank to choose all
glimpse(wages_clean)
```

### Plotting Box Plots

#### Questions to ask regarding the data set

1.  What is the basic distribution of realrinc?

```{r}
wages_clean %>%
  gf_boxplot(realrinc ~ "Income") %>% # Dummy X-axis "variable"
  gf_labs(
    title = "Plot 1A: Income has a skewed distribution",
    subtitle = "Many outliers on the high side"
  )
```

-   We infer that income is very skewed distribution.

2.  Is the realrinc affected by gender?

```{r}
wages_clean %>%
  gf_boxplot(gender ~ realrinc) %>%
  gf_labs(title = "Plot 2A: Income by Gender")
```

```{r}
wages_clean %>%
  gf_boxplot(gender ~ log10(realrinc), fill = "pink") %>%
  gf_labs(title = "Plot 2B: Log(Income) by Gender")
```

```{r}
wages_clean %>%
  gf_boxplot(gender ~ realrinc, fill = ~gender) %>%
  gf_refine(scale_x_log10()) %>%
  gf_labs(title = "Plot 2C: Income filled by Gender, log scale") %>% 
    gf_refine(scale_fill_manual(values = c("powderblue", "pink")))
```

> **The difference between log10 and scale_x_log10, is that when we use log 10, we convert the x-axis values into log values, but when we use scale, we increase the width of the x-axis (scale of x-axis).**

-   The inter quartile range for males is smaller than females. There are less variations in the median for men.

-   There are outliers in both the sides of the graph, which shows that there are a significant amount people who have a smaller income and some who have a larger income.

3.  Is realrinc affected by educcat?

```{r}
wages_clean %>%
  gf_boxplot(educcat ~ realrinc) %>%
  gf_labs(title = "Plot 3A: Income by Education Category") 
```

-   This graph shows income of people who have different kinds of education attainments.

-   A graduate has a higher income compared to others.

-   There are outliers on the positive side, which shows that there are a significant amount of people who have a higher income regardless of the degree of education they have.

```{r}
wages_clean %>%
  gf_boxplot(educcat ~ log10(realrinc)) %>%
  gf_labs(title = "Plot 3B: Log(Income) by Education Category") %>% 
```

```{r}
wages_clean %>%
  gf_boxplot(
    reorder(educcat, realrinc, FUN = median) ~ log(realrinc),
    fill = ~educcat,
    alpha = 0.3
  ) %>%
  gf_labs(title = "Plot 3C: Log(Income) by Education Category, sorted") %>%
  gf_labs(
    x = "Log Income",
    y = "Education Category"
  )
```

```{r}
wages_clean %>%
  gf_boxplot(reorder(educcat, realrinc, FUN = median) ~ realrinc,
    fill = ~educcat,
    alpha = 0.5
  ) %>%
  gf_refine(scale_x_log10()) %>%
  gf_labs(
    title = "Plot 3D: Income by Education Category, sorted",
    subtitle = "Log Income"
  ) %>%
  gf_labs(
    x = "Income",
    y = "Education Category"
  )
```

-   We infer that, there are outliers on the negative side, which gives us more insight on the fact that educcat does affect the income.

-   But there are also people with really small and really large income as there are outliers on both the sides.

-   A higher education returns a higher income, as expected.

4.  Is the target variable realrinc affected by combinations of Qual factors gender, educcat, maritalcat, childs?

```{r}
wages %>%
  drop_na() %>%
  gf_boxplot(reorder(educcat, realrinc) ~ log10(realrinc),
    fill = ~educcat,
    alpha = 0.5
  ) %>%
  gf_facet_wrap(vars(childs)) %>%
  gf_refine(scale_fill_brewer(type = "qual", palette = "Dark2")) %>%
  gf_labs(
    title = "Plot 4A: Log Income by Education Category and Family Size",
    x = "Log income",
    y = "No. of Children"
  )
```

```{r}
wages %>%
  drop_na() %>%
  mutate(childs = as_factor(childs)) %>%
  gf_boxplot(childs ~ log10(realrinc),
    group = ~childs,
    fill = ~childs,
    alpha = 0.5
  ) %>%
  gf_facet_wrap(~gender) %>%
  gf_refine(scale_fill_brewer(type = "qual", palette = "Set3")) %>%
  gf_labs(
    title = "Plot 4B: Log Income by Gender and Family Size",
    x = "Log income",
    y = "No. of Children"
  )
```

-   Realrinc increases with educcat in all family sizes.

-   For females, the income reduces with the no. of children and for males it increases till around 4 children.

-   The affect educcat and gender has on income is different.
