---
title: "Class-5(Change)"
author: "Anusha"
date: "10-10-24"
---

# Class-5 (Change)

# Part two

## Introduction

*The second module for today is Change. 'Change' is used to find some association between variables.*

-   In this section, we are going to plot a quant v/s quant.

-   To do this we need to understand something called 'Correlation'.

```{r}
#| label: setup
library(tidyverse) # Tidy data processing and plotting
library(ggformula) # Formula based plots
library(mosaic) # Our go-to package
library(skimr) # Another Data inspection package
library(kableExtra) # Making good tables with data

library(GGally) # Corr plots
library(corrplot) # More corrplots
library(ggExtra) # Making Combination Plots

# devtools::install_github("rpruim/Lock5withR")
library(Lock5withR) # Datasets
library(palmerpenguins) # A famous dataset

library(easystats) # Easy Statistical Analysis and Charts
library(correlation) # Different Types of Correlations
# From the easystats collection of packages
```

#### What is 'Correlation'?

-   In statistical terms, we use correlation to denote association between two quant variables.

-   Usually, this association is linear, as in if there is a unit increase/decrease in x, there will be a unit increase/decrease in y. This doesn't necessarily have to be directly proportional.

-   There is another technique called 'regression', which is used to estimate the best straight line to summarize the association between the variables.

-   The degree of association is measured by a correlation coefficient. This is measured using Z scores.

    -   This is done by multiplying the Z score of the x variable to the Z score of the y variable and dividing them by their standard deviation and then averaging it out.

```{r}
HollywoodMovies2011 -> movies
glimpse(movies)
```

```{r}
skim(movies)
```

```{r}
inspect(movies)
```

### Scatter Plots

```{r}
movies %>%
  gf_point(DomesticGross ~ WorldGross) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Movie Gross Earnings: Domestics vs World"
  )
```

```{r}
movies %>%
  gf_point(Profitability ~ OpeningWeekend) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Movies: Does Opening Week Earnings indicate Profitability?"
  )
```

```{r}
movies %>%
  gf_point(RottenTomatoes ~ AudienceScore) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Movie Ratings: Tomatoes vs Audience"
  )
```

```{r}
movies %>%
  drop_na() %>%
  gf_point(RottenTomatoes ~ AudienceScore,
    color = ~Genre
  ) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Movie Ratings: Trends by Genre"
  )
```

### Quantizing Correlation

'GGally::ggpairs' provides:

-   two different comparisons of each pair of columns

-   displays either the density or count of the respective variable along the diagonal. 

-   With different parameter settings, the diagonal can be replaced with the axis values and variable labels.

```{r}
GGally::ggpairs(
  movies %>% drop_na(),
  # Select Quant variables only for now
  columns = c(
    "RottenTomatoes", "AudienceScore", "DomesticGross", "ForeignGross"
  ),
  switch = "both",
  # axis labels in more traditional locations(left and bottom)

  progress = FALSE,
  # no compute progress messages needed

  # Choose the diagonal graphs (always single variable! Think!)
  diag = list(continuous = "barDiag"),
  # choosing histogram,not density

  # Choose lower triangle graphs, two-variable graphs
  lower = list(continuous = wrap("smooth", alpha = 0.3, se = FALSE)),
  title = "Movies Data Correlations Plot #1"
)
```

```{r}
GGally::ggpairs(
  movies %>% drop_na(),
  # Select Quant variables only for now
  columns = c(
    "Budget", "Profitability", "DomesticGross", "ForeignGross"
  ),
  switch = "both",
  # axis labels in more traditional locations(left and bottom)

  progress = FALSE,
  # no compute progress messages needed

  # Choose the diagonal graphs (always single variable! Think!)
  diag = list(continuous = "barDiag"),
  # choosing histogram,not density

  # Choose lower triangle graphs, two-variable graphs
  lower = list(continuous = wrap("smooth", alpha = 0.3, se = FALSE)),
  title = "Movies Data Correlations Plot #2"
)
```

#### Doing a Correlation test

We use this code to obtain correlation scores.

```{r}
mosaic::cor_test(Profitability ~ Budget, data = movies) %>%
  broom::tidy() %>%
  knitr::kable(
    digits = 2,
    caption = "Movie Profitability vs Budget"
  )
```

```{r}
mosaic::cor_test(DomesticGross ~ Budget, data = movies) %>%
  broom::tidy() %>%
  knitr::kable(
    digits = 2,
    caption = "Movie Domestic Gross vs Budget"
  )
```

```{r}
mosaic::cor_test(ForeignGross ~ Budget, data = movies) %>%
  broom::tidy() %>%
  knitr::kable(
    digits = 2,
    caption = "Movie Foreign Gross vs Budget"
  )
```

### ErrorBar Plots for Correlation

```{r}
glimpse(mtcars)
```

```{r}
cor <- correlation::correlation(mtcars)
cor
```

```{r}
cor %>%
  # Filter for target variable `mpg` and plot
  filter(Parameter1 == "mpg") %>%
  gf_point(r ~ reorder(Parameter2, r), size = 4) %>%
  gf_errorbar(CI_low + CI_high ~ reorder(Parameter2, r),
    width = 0.5
  ) %>%
  gf_hline(yintercept = 0, color = "grey", linewidth = 2) %>%
  gf_labs(
    title = "Correlation Errorbar Chart",
    subtitle = "Target variable: mpg",
    x = "Predictor Variable",
    y = "Correlation Score with mpg"
  )
```

### New Combination Plot

#### Data set - Penguins

```{r}
penguins
```

```{r}
library(ggExtra)

penguins %>%
  drop_na() %>%
  gf_point(body_mass_g ~ flipper_length_mm, colour = ~species) %>%
  gf_smooth(method = "lm") %>%
  gf_refine(scale_colour_brewer(palette = "Accent")) %>%
  gf_labs(title = "Scatter Plot with Marginal Densities") %>%
  ggExtra::ggMarginal(
    type = "density", groupColour = TRUE,
    groupFill = TRUE, margins = "both"
  )
```

-   From this plot, we infer that when the body mass increases, the flipper length also increases.

    -   So, the Gento species have a higher body mass with a longer flipper length.

-   We can also see that there is a positive correlation due to the straight line for each species in the graph.

-   We also notice, that the Gento and the Chinstrip species is skewed. The Adelie species are kind of symmetrical.
