---
title: "Online-Class-1-Space"
author: "Anusha"
---

# Space

## Introduction

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
library(tmap)
library(osmdata)
library(rnaturalearth)
library(ggformula)
```

### Kinds of Geospatial Data

-   Point: Buildings, offices, venues,etc.

-   LineString: Roads, rivers, railways, etc.

-   Polygon: Lake, golf course, border of a country

-   MultiPolygon: Any non-contiguous set of area

Each cell contains a shape (polygon) for a map.

### Introduction to Maps

Steps in making maps:

1.  Search for an area of interest.
2.  Learn how to access spatial/map data using osmdata
3.  Plot and dress up our map using ggplot and tmap.

**Step 1: Specifying an area**

-   Locate the place of interest using the search box.

bbox: Bounding Box is a rectangular area you are interested in.

```{r}
bbox_1 <- matrix(
  c(77.574028, 12.917262, 77.595073, 12.939895),
  byrow = FALSE,
  nrow = 2,
  ncol = 2,
  dimnames = list(c('x', 'y'), c('min', 'max'))
)
bbox_1
```

-\> Using a place name to look up a Bounding Box with osmdata::getbb. This may not always work if the place name is well known.

```{r}
bbox_2 <- osmdata::getbb("Jayanagar, Bangalore, India")
bbox_2
```

**Step 2: Get Map Data**

OpenStreetMap (OSM) provides maps of the world mostly created by volunteers.

```{r}
locations <- 
  osmdata::opq(bbox = bbox_2) %>% 
  osmdata::add_osm_feature(key = "amenity", 
                           value = c("restaurant", "atm", "college")) %>% 
  osmdata_sf() %>%  # Convert to Simple Features format
  purrr::pluck("osm_points") # Pull out the data frame of interest

# Get all buildings within my bbox
dat_buildings <-
  osmdata::opq(bbox = bbox_2) %>% 
  osmdata::add_osm_feature(key = "building") %>% 
  osmdata_sf() %>% 
  purrr::pluck("osm_polygons") 


```

```{r}
str(locations)
str(dat_buildings)
```

```{r}
ggplot() +
  geom_sf(data = locations, fill = "gold", color = "grey", linewidth = 0.025)+    # POLYGONS
  geom_sf(data = dat_buildings, fill = "purple") 
```
